### 2024-08-11 my_paper/tables/tab04-summary-stats.tex
change latex doc and pdf to incorporate new changes
new edits

\begin{landscape}
\begin{ThreePartTable}
\begin{TableNotes}
\item[1] Source: The 1950-2000 Census for synthetic parents, and 1994-2019 Current Population Surveys (CPS) for children's outcomes
\item[2] The data is restricted to native-born United States citizens between 1994 and 2019 who are also White and between the ages of 25 and 40. I identify the ethnicity of a person's parents through the parent's place of birth. A parent is Hispanic if they were born in a Spanish-speaking country. A parent is White if they were born in the United States.
\end{TableNotes}
\begin{longtable}[t]{>{\raggedright\arraybackslash}p{5cm}cccccc}
\caption{Summary statistics of outcomes using parent's place of birth only for those that self-identify as Hispanic \label{tab:c&p2}}\\
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Father's and Mother's Ethnicities} & \multicolumn{2}{c}{Differences} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-7}
Variables & \specialcell{White \\ White \\ (WW) \\ (1)} & \specialcell{White \\ Hispanic \\ (WH) \\ (2)} & \specialcell{Hispanic \\ White \\ (HW) \\ (3)} & \specialcell{Hispanic \\ Hispanic \\ (HH) \\ (4)} & \specialcell{HH - WW \\ (5)} & \specialcell{HW - WH \\ (6)}\\
\midrule
\endfirsthead
\caption[]{Summary statistics of outcomes using parent's place of birth only for those that self-identify as Hispanic  \textit{(continued)}}\\
\toprule
Variables & \specialcell{White \\ White \\ (WW) \\ (1)} & \specialcell{White \\ Hispanic \\ (WH) \\ (2)} & \specialcell{Hispanic \\ White \\ (HW) \\ (3)} & \specialcell{Hispanic \\ Hispanic \\ (HH) \\ (4)} & \specialcell{HH - WW \\ (5)} & \specialcell{HW - WH \\ (6)}\\
\midrule
\endhead
\midrule
\multicolumn{7}{r@{}}{\textit{(Continued on Next Page...)}}\
\endfoot
\bottomrule
\insertTableNotes
\endlastfoot
\textbf{Panel A: Children's Education} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hspace{1em}Men’s education (Total Years) & \specialcell{13.82\\(2.42)} & \specialcell{13.4\\(2.38)} & \specialcell{13.08\\(2.27)} & \specialcell{12.87\\(2.3)} & \specialcell{-0.94***\\(0.01)} & \specialcell{-0.32**\\(0.03)}\\
\hspace{1em}Women’s education (Total Years) & \specialcell{14.06\\(2.37)} & \specialcell{13.62\\(2.39)} & \specialcell{13.26\\(2.35)} & \specialcell{13.22\\(2.39)} & \specialcell{-0.84***\\(0.01)} & \specialcell{-0.36**\\(0.02)}\\
\textbf{Panel B: Children's Employment and Earnings} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hspace{1em}Men’s Unemployment Rate & \specialcell{0.04\\(0.8)} & \specialcell{0.06\\(0.76)} & \specialcell{0.07\\(0.74)} & \specialcell{0.07\\(0.75)} & \specialcell{0.02***\\(0.00)} & \specialcell{0.01***\\(0.00)}\\
\addlinespace
\hspace{1em}Women’s Unemployment Rate & \specialcell{0.04\\(0.81)} & \specialcell{0.06\\(0.24)} & \specialcell{0.07\\(0.75)} & \specialcell{0.06\\(0.76)} & \specialcell{0.02***\\(0.00)} & \specialcell{0.01***\\(0.00)}\\
\hspace{1em}Men’s Log Hourly Earnings & \specialcell{2.51\\(0.45)} & \specialcell{2.43\\(0.46)} & \specialcell{2.42\\(0.44)} & \specialcell{2.42\\(0.43)} & \specialcell{-0.09***\\(0)} & \specialcell{-0.00**\\(0.02)}\\
\hspace{1em}Women’s Log Hourly Earnings & \specialcell{2.32\\(0.49)} & \specialcell{2.31\\(0.45)} & \specialcell{2.28\\(0.45)} & \specialcell{2.31\\(0.42)} & \specialcell{-0.02***\\(0)} & \specialcell{-0.03**\\(0.02)}\\
\hspace{1em}Men’s Log Annual Earnings & \specialcell{10.29\\(1.01)} & \specialcell{10.09\\(1.05)} & \specialcell{10.06\\(0.97)} & \specialcell{10.01\\(1.04)} & \specialcell{-0.28***\\(0.01)} & \specialcell{-0.03**\\(0.03)}\\
\hspace{1em}Women’s Log Annual Earnings & \specialcell{9.43\\(1.77)} & \specialcell{9.52\\(1.59)} & \specialcell{9.47\\(1.56)} & \specialcell{9.53\\(1.49)} & \specialcell{0.1**\\(0.02)} & \specialcell{-0.05*\\(0.05)}\\*
\end{longtable}
\end{ThreePartTable}
\end{landscape}

>>>>

\begin{landscape}
\begin{ThreePartTable}
\begin{TableNotes}
\item[1] Source: The 1994-2019 Current Population Surveys (CPS) for children's outcomes
\item[2] The data is restricted to native-born United States citizens between 1994 and 2019 who are also White and between the ages of 25 and 40. The summary statistics for White-Hispanic (WH), Hispanic-White (HW), and Hispanic-Hispanic (HH) are restricted to the sample of children that self-identify as Hispanic or Latino. I identify the ethnicity of a person's parents through the parent's place of birth. A parent is Hispanic if they were born in a Spanish-speaking country. A parent is White if they were born in the United States.
\end{TableNotes}
\begin{longtable}[t]{>{\raggedright\arraybackslash}p{5cm}cccccc}
\caption{Summary Statistics of Outcomes Using Parent's Place of Birth Only for Those That Self-Identify as Hispanic \label{tab:c&p2}}\\
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Father's and Mother's Ethnicities} & \multicolumn{2}{c}{Differences} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-7}
Variables & \specialcell{White \\ White \\ (WW) \\ (1)} & \specialcell{White \\ Hispanic \\ (WH) \\ (2)} & \specialcell{Hispanic \\ White \\ (HW) \\ (3)} & \specialcell{Hispanic \\ Hispanic \\ (HH) \\ (4)} & \specialcell{HH - WW \\ (5)} & \specialcell{HW - WH \\ (6)}\\
\midrule
\endfirsthead
\caption[]{Summary Statistics of Outcomes Using Parent's Place of Birth Only for Those That Self-Identify as Hispanic  \textit{(continued)}}\\
\toprule
Variables & \specialcell{White \\ White \\ (WW) \\ (1)} & \specialcell{White \\ Hispanic \\ (WH) \\ (2)} & \specialcell{Hispanic \\ White \\ (HW) \\ (3)} & \specialcell{Hispanic \\ Hispanic \\ (HH) \\ (4)} & \specialcell{HH - WW \\ (5)} & \specialcell{HW - WH \\ (6)}\\
\midrule
\endhead
\midrule
\multicolumn{7}{r@{}}{\textit{(Continued on Next Page...)}}\\
\endfoot
\bottomrule
\insertTableNotes
\endlastfoot
\textbf{Panel A: Children's Education} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hspace{1em}Men’s education (Total Years) & \specialcell{13.82\\(2.42)} & \specialcell{13.4\\(2.38)} & \specialcell{13.07\\(2.27)} & \specialcell{12.87\\(2.3)} & \specialcell{-0.94***\\(0.01)} & \specialcell{-0.32**\\(0.03)}\\
\hspace{1em}Women’s education (Total Years) & \specialcell{14.06\\(2.37)} & \specialcell{13.62\\(2.39)} & \specialcell{13.26\\(2.35)} & \specialcell{13.22\\(2.39)} & \specialcell{-0.84***\\(0.01)} & \specialcell{-0.36**\\(0.02)}\\
\hspace{1em}Men’s Highschool Dropout Rate & \specialcell{0.35\\(0.48)} & \specialcell{0.45\\(0.5)} & \specialcell{0.44\\(0.5)} & \specialcell{0.44\\(0.5)} & \specialcell{0.09***\\(0)} & \specialcell{-0.01***\\(0.01)}\\
\hspace{1em}Women’s Highschool Dropout Rate & \specialcell{0.36\\(0.48)} & \specialcell{0.45\\(0.5)} & \specialcell{0.46\\(0.5)} & \specialcell{0.46\\(0.5)} & \specialcell{0.1***\\(0)} & \specialcell{0.01***\\(0.01)}\\
\addlinespace
\hspace{1em}Men’s Associate Degree Rate & \specialcell{0.15\\(0.36)} & \specialcell{0.15\\(0.36)} & \specialcell{0.12\\(0.32)} & \specialcell{0.11\\(0.32)} & \specialcell{-0.03***\\(0)} & \specialcell{-0.03***\\(0)}\\
\hspace{1em}Women’s Associate Degree Rate & \specialcell{0.19\\(0.39)} & \specialcell{0.17\\(0.37)} & \specialcell{0.14\\(0.35)} & \specialcell{0.15\\(0.36)} & \specialcell{-0.04***\\(0)} & \specialcell{-0.03***\\(0)}\\
\hspace{1em}Men’s BA Degree Rate & \specialcell{0.32\\(0.47)} & \specialcell{0.23\\(0.42)} & \specialcell{0.19\\(0.39)} & \specialcell{0.17\\(0.38)} & \specialcell{-0.15***\\(0)} & \specialcell{-0.04***\\(0.01)}\\
\hspace{1em}Women’s BA Degree Rate & \specialcell{0.36\\(0.48)} & \specialcell{0.28\\(0.45)} & \specialcell{0.22\\(0.41)} & \specialcell{0.22\\(0.41)} & \specialcell{-0.14***\\(0)} & \specialcell{-0.06***\\(0)}\\
\hspace{1em}Men’s Professional Degree Rate & \specialcell{0.09\\(0.28)} & \specialcell{0.07\\(0.25)} & \specialcell{0.05\\(0.21)} & \specialcell{0.04\\(0.19)} & \specialcell{-0.05***\\(0)} & \specialcell{-0.02***\\(0)}\\
\addlinespace
\hspace{1em}Women’s Professional Degree Rate & \specialcell{0.1\\(0.3)} & \specialcell{0.08\\(0.26)} & \specialcell{0.07\\(0.25)} & \specialcell{0.06\\(0.23)} & \specialcell{-0.04***\\(0)} & \specialcell{-0.01***\\(0)}\\
\textbf{Panel B: Children's Employment and Earnings} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
\hspace{1em}Men’s Unemployment Rate & \specialcell{0.04\\(0.8)} & \specialcell{0.06\\(0.76)} & \specialcell{0.07\\(0.74)} & \specialcell{0.07\\(0.75)} & \specialcell{0.02***\\(0.00)} & \specialcell{0.01***\\(0.00)}\\
\hspace{1em}Women’s Unemployment Rate & \specialcell{0.04\\(0.81)} & \specialcell{0.06\\(0.24)} & \specialcell{0.07\\(0.75)} & \specialcell{0.06\\(0.76)} & \specialcell{0.02***\\(0.00)} & \specialcell{0.01***\\(0.00)}\\
\hspace{1em}Men’s Log Hourly Earnings & \specialcell{2.51\\(0.45)} & \specialcell{2.43\\(0.46)} & \specialcell{2.42\\(0.44)} & \specialcell{2.42\\(0.43)} & \specialcell{-0.09***\\(0)} & \specialcell{-0.00**\\(0.02)}\\
\addlinespace
\hspace{1em}Women’s Log Hourly Earnings & \specialcell{2.32\\(0.49)} & \specialcell{2.31\\(0.45)} & \specialcell{2.28\\(0.45)} & \specialcell{2.31\\(0.42)} & \specialcell{-0.02***\\(0)} & \specialcell{-0.03**\\(0.02)}\\
\hspace{1em}Men’s Log Annual Earnings & \specialcell{10.29\\(1.01)} & \specialcell{10.09\\(1.05)} & \specialcell{10.06\\(0.97)} & \specialcell{10.01\\(1.04)} & \specialcell{-0.28***\\(0.01)} & \specialcell{-0.03**\\(0.03)}\\
\hspace{1em}Women’s Log Annual Earnings & \specialcell{10.13\\(0.78)} & \specialcell{10.04\\(0.79)} & \specialcell{10.02\\(0.72)} & \specialcell{10.01\\(0.73)} & \specialcell{-0.12***\\(0.01)} & \specialcell{-0.02**\\(0.03)}\\*
\end{longtable}
\end{ThreePartTable}
\end{landscape}

### 2024-08-11 output/tables/tab02-observations-by-couple.tex
new edits

\begin{table}[H]

\caption{Couples' Type \label{tab:mat2}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{>{}lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Couples Type} \\
\cmidrule(l{3pt}r{3pt}){2-5}
  & \specialcell{White Husband \\ White Wife} & \specialcell{White Husband \\ Hispanic Wife} & \specialcell{Hispanic Husband \\ White Wife} & \specialcell{Hispanic Husband \\ Hispanic Wife}\\
\midrule
\textbf{\specialcell{Observations\\Share}} & \specialcell{1,286,731\\0.97} & \specialcell{7,178\\0.01} & \specialcell{7,606\\0.01} & \specialcell{20,911\\0.02}\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[1] Source: 1970-1990 Census
\item[2] The sample includes Whites, who are married, and are between the ages 25 and 40. Ethnicity of a person's parents are identified by the parent's place of birth. A parent is Hispanic if she/he was born in a Spanish-speaking country. A parent is White she/he was born in the United States.
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Couples' Type \label{tab:mat2}}
\centering
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{threeparttable}
\begin{tabular}[t]{>{}lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Couples Type} \\
\cmidrule(l{3pt}r{3pt}){2-5}
  & \specialcell{White Husband \\ White Wife} & \specialcell{White Husband \\ Hispanic Wife} & \specialcell{Hispanic Husband \\ White Wife} & \specialcell{Hispanic Husband \\ Hispanic Wife}\\
\midrule
\textbf{\specialcell{Observations\\Share}} & \specialcell{5,141,737\\0.96} & \specialcell{33,097\\0.01} & \specialcell{37,847\\0.01} & \specialcell{119,749\\0.02}\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[1] Source: 1960-2000 Census
\item[2] The sample includes Whites, who are married, with kids, and are between the ages 25 and 40. Ethnicity of a person's parents are identified by the parent's place of birth. A parent is Hispanic if she/he was born in a Spanish-speaking country. A parent is White if she/he was born in the United States.
\end{tablenotes}
\end{threeparttable}}
\end{table}

### 2024-08-11 output/tables/tab05-regression.tex
new edits

\begin{table}[H]

\caption{Effect of Having Hispanic Last Name \label{tab:lastnamereg}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ Log annual \\ earnings} & \specialcell{(2) \\ Log annual \\ earnings} & \specialcell{(3) \\ Log annual \\ earnings} & \specialcell{(4) \\  Log annual \\ earnings}\\
\midrule
$HW_{ist}$ & \num{-0.06}** & \num{-0.07}** & \num{-0.05}** & \num{-0.02}\\
 & (\num{0.03}) & (\num{0.03}) & (\num{0.02}) & (\num{0.02})\\
Constant & \num{10.40}*** & \num{9.49}*** &  & \\
 & (\num{0.04}) & (\num{0.07}) &  & \\
\midrule
\textit{Controlling for:} &  &  &  & \\
Hours Worked &  & X & X & X\\
State FE &  &  & X & X\\
Year FE &  &  & X & X\\
Age FE &  &  & X & X\\
Education FE &  &  &  & X\\
Observations & \num{2423} & \num{2423} & \num{2423} & \num{2423}\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] {\setstretch{1.0}\footnotesize{This table includes the estimation results of equation (\ref{eq:1a}).}}
\item[2] {\setstretch{1.0}\footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}}
\item[3] {\setstretch{1.0}\footnotesize{The sample is restricted to men working full-time full-year and are wage and salary workers.}}
\item[4] {\setstretch{1.0}\footnotesize{Column one has the regression results when controlling for hours worked, age, education, year and state fixed effects. Column two has the results after controlling for education.}}
\item[5] {\setstretch{1.0}\footnotesize{Standard errors are clustered on the state level.}}
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Effect of Having Hispanic Last Name (Log Annual Earnings) \label{tab:lastnamereg}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lccccc}
\toprule
  & \specialcell{(1) \\ Log annual \\ earnings} & \specialcell{(2) \\ Log annual \\ earnings} & \specialcell{(3) \\ Log annual \\ earnings} & \specialcell{(4) \\  Log annual \\ earnings} & \specialcell{(5) \\  Log annual \\ earnings}\\
\midrule
$HW_{ist}$ & \num{-0.05}*** & \num{-0.05}** & \num{-0.05}* & \num{-0.02} & \num{-0.01}\\
 & (\num{0.02}) & (\num{0.02}) & (\num{0.02}) & (\num{0.02}) & (\num{0.02})\\
Constant & \num{10.42}*** & \num{9.46}*** &  &  & \\
 & (\num{0.04}) & (\num{0.07}) &  &  & \\
\midrule
\textit{Controlling for:} &  &  &  &  & \\
Hours Worked &  & X & X & X & X\\
Age &  &  & X & X & X\\
State FE &  &  & X & X & X\\
Year FE &  &  & X & X & X\\
State-Year FE &  &  & X & X & X\\
Education &  &  &  & X & X\\
Parental Background &  &  &  &  & X\\
Observations & \num{3621} & \num{3621} & \num{3621} & \num{3621} & \num{3621}\\
\bottomrule
\multicolumn{6}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] {\setstretch{1.0}\footnotesize{This table includes the estimation results of equation (\ref{eq:1a}).}}
\item[2] {\setstretch{1.0}\footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}}
\item[3] {\setstretch{1.0}\footnotesize{The sample is restricted to men working full-time full-year and are wage and salary workers.}}
\item[4] {\setstretch{1.0}\footnotesize{Column one has the regression results when controlling for hours worked, age, education, year and state fixed effects. Column two has the results after controlling for education.}}
\item[5] {\setstretch{1.0}\footnotesize{Standard errors are clustered on the state level.}}
\end{tablenotes}
\end{threeparttable}
\end{table}

### 2024-08-11 output/tables/tab09-regression-weekearn-nonmex.tex
new edits

\begin{table}[H]

\caption{Effect of Having Hispanic Last Name: Hispanics with Non-Mexican Ancestry  \label{tab:lastnamereg-weekearm-nonmex}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ Log weekly \\ earnings} & \specialcell{(2) \\ Log weekly \\ earnings} & \specialcell{(3) \\  Log weekly \\ earnings} & \specialcell{(4) \\  Log weekly \\ earnings}\\
\midrule
$HW_{ist}$ & \num{-0.04} & \num{-0.04} & \num{-0.01} & \num{-0.01}\\
 & (\num{0.03}) & (\num{0.02}) & (\num{0.02}) & (\num{0.03})\\
Constant & \num{6.71}*** &  &  & \\
 & (\num{0.03}) &  &  & \\
\midrule
\textit{Controlling for:} &  &  &  & \\
State FE &  & X & X & X\\
Year FE &  & X & X & X\\
Age FE &  & X & X & X\\
Education FE &  &  & X & X\\
Parental Background &  &  &  & X\\
Observations & \num{2859} & \num{2859} & \num{2859} & \num{2859}\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] {\setstretch{1.0}\footnotesize{This table includes the estimation results of equation (\ref{eq:1a}) where the dependent variable is log weekly earnings.}}
\item[2] {\setstretch{1.0}\footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}}
\item[3] {\setstretch{1.0}\footnotesize{The sample is restricted to men working full-time and are wage and salary workers.}}
\item[4] {\setstretch{1.0}\footnotesize{Column one has the regression results when controlling for hours worked, age, education, year and state fixed effects. Column two has the results after controlling for education.}}
\item[5] {\setstretch{1.0}\footnotesize{Standard errors are clustered on the state level.}}
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Effect of Having Hispanic Last Name: Hispanics with Non-Mexican Ancestry  \label{tab:lastnamereg-weekearm-nonmex}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ Log weekly \\ earnings} & \specialcell{(2) \\ Log weekly \\ earnings} & \specialcell{(3) \\  Log weekly \\ earnings} & \specialcell{(4) \\  Log weekly \\ earnings}\\
\midrule
$HW_{ist}$ & \num{-0.04} & \num{-0.07}** & \num{-0.03} & \num{-0.03}\\
 & (\num{0.03}) & (\num{0.03}) & (\num{0.03}) & (\num{0.03})\\
Constant & \num{6.70}*** &  &  & \\
 & (\num{0.03}) &  &  & \\
\midrule
\textit{Controlling for:} &  &  &  & \\
State FE &  & X & X & X\\
Year FE &  & X & X & X\\
State-Year FE &  & X & X & X\\
Age &  & X & X & X\\
Education &  &  & X & X\\
Parental Background &  &  &  & X\\
Observations & \num{2853} & \num{2853} & \num{2853} & \num{2853}\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] {\setstretch{1.0}\footnotesize{This table includes the estimation results of equation (\ref{eq:1a}) where the dependent variable is log weekly earnings.}}
\item[2] {\setstretch{1.0}\footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}}
\item[3] {\setstretch{1.0}\footnotesize{The sample is restricted to men working full-time and are wage and salary workers.}}
\item[4] {\setstretch{1.0}\footnotesize{Column one has the regression results when controlling for hours worked, age, education, year and state fixed effects. Column two has the results after controlling for education.}}
\item[5] {\setstretch{1.0}\footnotesize{Standard errors are clustered on the state level.}}
\end{tablenotes}
\end{threeparttable}
\end{table}

### 2024-08-11 output/tables/tab10-regression-weekearn-cuba.tex
new edits

\begin{table}[H]

\caption{Effect of Having Hispanic Last Name: Hispanics with Cuban Ancestry  \label{tab:lastnamereg-weekearm-cub}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ Log weekly \\ earnings} & \specialcell{(2) \\ Log weekly \\ earnings} & \specialcell{(3) \\  Log weekly \\ earnings} & \specialcell{(4) \\  Log weekly \\ earnings}\\
\midrule
$HW_{ist}$ & \num{-0.08}** & \num{-0.03} & \num{-0.01} & \num{-0.02}\\
 & (\num{0.04}) & (\num{0.04}) & (\num{0.04}) & (\num{0.05})\\
Constant & \num{6.69}*** &  &  & \\
 & (\num{0.05}) &  &  & \\
\midrule
\textit{Controlling for:} &  &  &  & \\
State FE &  & X & X & X\\
Year FE &  & X & X & X\\
Age FE &  & X & X & X\\
Education FE &  &  & X & X\\
Parental Background &  &  &  & X\\
Observations & \num{1182} & \num{1182} & \num{1182} & \num{1182}\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] {\setstretch{1.0}\footnotesize{This table includes the estimation results of equation (\ref{eq:1a}) where the dependent variable is log weekly earnings.}}
\item[2] {\setstretch{1.0}\footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}}
\item[3] {\setstretch{1.0}\footnotesize{The sample is restricted to men working full-time and are wage and salary workers.}}
\item[4] {\setstretch{1.0}\footnotesize{Column one has the regression results when controlling for hours worked, age, education, year and state fixed effects. Column two has the results after controlling for education.}}
\item[5] {\setstretch{1.0}\footnotesize{Standard errors are clustered on the state level.}}
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Effect of Having Hispanic Last Name: Hispanics with Cuban Ancestry  \label{tab:lastnamereg-weekearm-cub}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ Log weekly \\ earnings} & \specialcell{(2) \\ Log weekly \\ earnings} & \specialcell{(3) \\  Log weekly \\ earnings} & \specialcell{(4) \\  Log weekly \\ earnings}\\
\midrule
$HW_{ist}$ & \num{-0.08}** & \num{-0.06} & \num{-0.02} & \num{-0.03}\\
 & (\num{0.04}) & (\num{0.06}) & (\num{0.05}) & (\num{0.05})\\
Constant & \num{6.68}*** &  &  & \\
 & (\num{0.05}) &  &  & \\
\midrule
\textit{Controlling for:} &  &  &  & \\
State FE &  & X & X & X\\
Year FE &  & X & X & X\\
State-Year FE &  & X & X & X\\
Age &  & X & X & X\\
Education &  &  & X & X\\
Parental Background &  &  &  & X\\
Observations & \num{1179} & \num{1179} & \num{1179} & \num{1179}\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] {\setstretch{1.0}\footnotesize{This table includes the estimation results of equation (\ref{eq:1a}) where the dependent variable is log weekly earnings.}}
\item[2] {\setstretch{1.0}\footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}}
\item[3] {\setstretch{1.0}\footnotesize{The sample is restricted to men working full-time and are wage and salary workers.}}
\item[4] {\setstretch{1.0}\footnotesize{Column one has the regression results when controlling for hours worked, age, education, year and state fixed effects. Column two has the results after controlling for education.}}
\item[5] {\setstretch{1.0}\footnotesize{Standard errors are clustered on the state level.}}
\end{tablenotes}
\end{threeparttable}
\end{table}

### 2024-08-11 output/tables/tab12-regression.tex
new edits

\begin{table}[H]
\centering\centering
\caption{Effect of Having Hispanic Last Name (Log Annual Earnings) \label{tab:lastnamereg}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lccccc}
\toprule
  & \specialcell{(1) \\ Log annual \\ earnings} & \specialcell{(2) \\ Log annual \\ earnings} & \specialcell{(3) \\ Log annual \\ earnings} & \specialcell{(4) \\  Log annual \\ earnings} & \specialcell{(5) \\  Log annual \\ earnings}\\
\midrule
$HW_{ist}$ & \num{-0.05}*** & \num{-0.05}** & \num{-0.05}* & \num{-0.02} & \num{-0.01}\\
 & (\num{0.02}) & (\num{0.02}) & (\num{0.02}) & (\num{0.02}) & (\num{0.02})\\
Constant & \num{10.42}*** & \num{9.46}*** &  &  & \\
 & (\num{0.04}) & (\num{0.07}) &  &  & \\
\midrule
\textit{Controlling for:} &  &  &  &  & \\
Hours Worked &  & X & X & X & X\\
Age &  &  & X & X & X\\
State FE &  &  & X & X & X\\
Year FE &  &  & X & X & X\\
State-Year FE &  &  & X & X & X\\
Education &  &  &  & X & X\\
Parental Background &  &  &  &  & X\\
Observations & \num{3621} & \num{3621} & \num{3621} & \num{3621} & \num{3621}\\
\bottomrule
\multicolumn{6}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] {\setstretch{1.0}\footnotesize{This table includes the estimation results of equation (\ref{eq:1a}).}}
\item[2] {\setstretch{1.0}\footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}}
\item[3] {\setstretch{1.0}\footnotesize{The sample is restricted to men working full-time full-year and are wage and salary workers.}}
\item[4] {\setstretch{1.0}\footnotesize{Column one has the regression results when controlling for hours worked, age, education, year and state fixed effects. Column two has the results after controlling for education.}}
\item[5] {\setstretch{1.0}\footnotesize{Standard errors are clustered on the state level.}}
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Effect of Having Hispanic Last Name \label{tab:lastnamereg}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lccccc}
\toprule
  & \specialcell{(1) \\ Log annual \\ earnings} & \specialcell{(2) \\ Log annual \\ earnings} & \specialcell{(3) \\ Log annual \\ earnings} & \specialcell{(4) \\  Log annual \\ earnings} & \specialcell{(5) \\  Log annual \\ earnings}\\
\midrule
$HW_{ist}$ & \num{-0.05}*** & \num{-0.05}** & \num{-0.05}* & \num{-0.02} & \num{-0.01}\\
 & (\num{0.02}) & (\num{0.02}) & (\num{0.02}) & (\num{0.02}) & (\num{0.02})\\
Constant & \num{10.42}*** & \num{9.46}*** &  &  & \\
 & (\num{0.04}) & (\num{0.07}) &  &  & \\
\midrule
\textit{Controlling for:} &  &  &  &  & \\
Hours Worked &  & X & X & X & X\\
Age &  &  & X & X & X\\
Education &  &  &  & X & X\\
NA & NA & NA & NA & NA & \vphantom{2} NA\\
NA & NA & NA & NA & NA & \vphantom{1} NA\\
NA & NA & NA & NA & NA & NA\\
Parental Background &  &  &  &  & X\\
Observations & \num{3621} & \num{3621} & \num{3621} & \num{3621} & \num{3621}\\
\bottomrule
\multicolumn{6}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\item[1] {\setstretch{1.0}\footnotesize{This table includes the estimation results of equation (\ref{eq:1a}).}}
\item[2] {\setstretch{1.0}\footnotesize{HW is an indicator variable that is equal to 1 if a person is the child of a Hispanic-father and White-mother.}}
\item[3] {\setstretch{1.0}\footnotesize{Standard errors are clustered on the state level.}}
\end{tablenotes}
\end{threeparttable}
\end{table}
